Propositions as Sessions, Mechanically

### 2015-04-12 paper/formalisation.tex
Minor tweaks.
Added the rest of GV's terms to figure.

Following informal proofs, it seems likely that the proof requires a
termination measure involving the length of the derivation. In hindsight,
however, I do not believe the current encoding is the best for this sort of
reasoning. Formalised efforts for proving cut elimination for other logics
have adopted an approach which permits reasoning on the structure of
derivations represented explicitly as
trees~\cite{Tews:2013,Dawson:2010,Dawson:2002}. Whereas, in the approach taken
here, that information is limited and ephemeral in that it is only available
during the proving of a derivation e.g. a reduction lemma. It is future work
to investigate these and other strategies which will assist in proving
cut-elimination for CP.

@@

All types are amalgamated into one inductive definition and provide a
predicate for restricting typing rules to consider only valid session
types. As shown in \S~\ref{sec:...}, \citeauthor{Wadler:2014} defines GV types
as a set of mutually recursive definitions. Unfortunately, handling mutually
inductive definitions in Coq can be quite involved, requiring one to either
rely on the Coq system to provide a stronger mutual induction principle or
define one manually. Such a definition is possible, but it complicates
applications of the induction principle.

>>>>

Following informal proofs, it seems likely that the proof requires a
termination measure involving the length of the derivation. In hindsight,
however, I do not believe the current encoding is the best for this sort of
reasoning. Formalised efforts for proving cut elimination for other logics
have adopted an approach which permits reasoning on the structure of
derivations represented explicitly as
trees~\cite{Tews:2013,Dawson:2010,Dawson:2002}. Whereas, in the approach taken
here, that information is limited and ephemeral in that it is only available
during the proving of a derivation e.g. a reduction lemma. It is future work
to investigate these and other strategies which will assist in formalising
cut-elimination for CP.

@@

All types are amalgamated into one inductive definition and provide a
predicate for restricting typing rules to consider only valid session
types. As shown in \S~\ref{sec:fusion}, \citeauthor{Wadler:2014} defines GV
types as a set of mutually recursive definitions. Unfortunately, handling
mutually inductive definitions in Coq can be quite involved, requiring one to
either rely on the Coq system to provide a stronger mutual induction principle
or define one manually. Such a definition is possible, but it complicates
applications of the induction principle.
